---
title: "chl-indicator-comparison-calculations"
author: "Matt Callahan"
date: "6/23/2022"
output: html_document
---

The actual calculations of the ESP indicators are performed here. First we will recalculate previously submitted indicators with MODIS data to ensure that we are using the correct processes. Then we will apply the same code to the OC-CCI data. We will compare indicators visually by plotting indicator values over time and against each other, and statistically with simple linear models.
## Load data
From chla-indicator-comparison-data.Rmd

**MODIS**
MODIS data were downloaded from a google folder where Jordan stored them from previous efforts https://drive.google.com/drive/u/1/folders/1mhwQ70mjLrkiQYiQ2oNHx08Q7IlL8Q3-

```{r}
#EBS
mod_ebs<-readRDS("Data/MODIS/merged_8day_2003_2021_EBS.RDS")
#GOA
mod_goa<-readRDS("Data/MODIS/merged_8day_2003_2021_GOA.RDS")
```

**Load oc-cci**
```{r}
occci_esp<-readRDS("Data/OCCCI/occ8_esp_strata.RDS")
```


## ESP indicators
These indicators were requested by stock assessment authors. Each indicator is a single value for each year.

**Previous ESP Indicator descriptions**
```{r}
#check which indicators were used
ind <- httr::content(httr::GET("https://apex.psmfc.org/akfin/data_marts/akmp/esp_indicators?"),
                      type = "application/json"
) %>%
  dplyr::bind_rows()

ind<-ind%>%filter(grepl('Chlorophylla', INDICATOR_NAME))

#all ours?
unique(ind$CONTACT) #yes

#Descriptions
ind%>%group_by(INDICATOR_NAME)%>%
  summarise(descritption=unique(PRODUCT_DESCRIPTION),
            submission_year=unique(SUBMISSION_YEAR))%>%
   flextable()%>%
  theme_box()

```

**functions**
Create functions for 

-comparing MODIS indicators with previous indicators
-joining MODIS and OC indicators
-plotting MODIS and OC indicators over time
-plotting MODIS and OC against each other 

```{r}
#Calculation will differ for each indicator so probably not worth functionalizing that. 

#Compare MODIS with previous indicator
#indicator is the INDICATOR_NAME in the ind object
#x is the data frame with the new MODIS indicator
pull_ind<-function(indicator, x) {
  ind%>%filter(INDICATOR_NAME==indicator)%>%
  dplyr::select(YEAR, DATA_VALUE)%>%
  left_join(x, by="YEAR")%>%
  mutate(diff=round(DATA_VALUE-MODIS_VALUE))%>%
    print()
}
#sum of differences
sumdiff<-function(x) {
  sum(x$diff)
}

#join
chla_join<-function(oc,mod) {
  occci%>% left_join(mod, by=c("year"="YEAR"))
}

#plot over time
chla_timeplot<-function(x, indicator) {
  x%>%
  ggplot()+
  geom_line(aes(x=year,y=OCCCI_VALUE), color="red")+
  geom_line(aes(x=year,y=MODIS_VALUE), color="blue")+
  ylab("chla")+
  ggtitle(paste(indicator, " OC-CCI=red, MODIS=blue"))
}

#equation functions
lm_eqn <- function(df){
    m <- lm(OCCCI_VALUE ~ MODIS_VALUE, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

chla_reg_plot<-function(df, indicator){
  ggplot(data=df, aes(x=MODIS_VALUE, y=OCCCI_VALUE, label=year))+
    geom_point()+
    geom_text()+
    geom_smooth(method="lm")+
    annotate(geom='text', label = lm_eqn(df), parse = TRUE, x=-Inf, y=Inf, hjust=0, vjust=1)+
    ggtitle(indicator)+
    geom_abline(slope=1, intercept=0, lty=2)
    
}

```

**AMJ_Chlorophylla_Biomass_SEBS_Satellite**


```{r}
#define indicator
indicator<-"AMJ_Chlorophylla_Biomass_SEBS_Satellite"
#MODIS
#recalculate indicator
mod_AMJ_SEBS <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(bsierp_name== "North middle shelf" & month%in%c(4:6)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_smbkc)
#Values different. Follow up with Jens

####NOT RUN####
sumdiff(temp)

#OC-cci
occci_smbkc<-occ_esp%>%
  filter(BS_KING=="StMattBKC" & month%in%c(4:6))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#join
smbkc_chla<-chla_join(occci_smbkc, mod_smbkc)

#plot
#timeseries
chla_timeplot(smbkc_chla, indicator)

#regression
fit<-lm_eqn(smbkc_chla)
chla_reg_plot(smbkc_chla, indicator)
```


**Spring_Chlorophylla_Biomass_EGOA_Satellite**
```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_EGOA_Satellite"
#MODIS
#recalculate indicator
mod_SPR_EGOA_B <- mod_goa %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(nmfsarea %in% c(640,650) & month==5 & depth<(-10) & depth>(-200)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_SPR_EGOA_B)
sumdiff(temp)

#Curious that this matches exactly when the indicator description says it uses oc-cci

#OCC
occci_SPR_EGOA_B<-occ_esp%>%
  filter(NMFS_REP_AREA%in% c(640, 650) & month==5 & depth<(-10) & depth>(-200))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#compare this to indicator
ind%>%filter(INDICATOR_NAME==indicator)%>%
  dplyr::select(YEAR, DATA_VALUE)%>%
  left_join(occci_SPR_EGOA_B, by=c("YEAR"="year"))%>%
  mutate(diff=round(DATA_VALUE-OCCCI_VALUE))%>%
    print()
#Nope...

#join
SPR_EGOA_B_chla<-chla_join(occci_SPR_EGOA_B, mod_SPR_EGOA_B)

#plot
#timeseries
chla_timeplot(SPR_EGOA_B_chla, indicator)

#regression
fit<-lm_eqn(SPR_EGOA_B_chla)
chla_reg_plot(SPR_EGOA_B_chla, indicator)


```

**Spring_Chlorophylla_Biomass_SEBS_Inner_Shelf_Satellite**


**Spring_Chlorophylla_Biomass_SEBS_Satellite**

**Spring_Chlorophylla_Biomass_SMBKC_Satellite**
Calculations from https://github.com/jordanwatson/ESP_Indicators/blob/main/ESP_Chlorophyll_Crab.R

```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_SMBKC_Satellite"
#MODIS
#recalculate indicator
mod_smbkc <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(crab=="StMatts" & month%in%c(4:6)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_smbkc)
sumdiff(temp)

#OCcci
occci_smbkc<-occ_esp%>%
  filter(BS_KING=="StMattBKC" & month%in%c(4:6))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#join
smbkc_chla<-chla_join(occci_smbkc, mod_smbkc)

#plot
#timeseries
chla_timeplot(smbkc_chla, indicator)

#regression
fit<-lm_eqn(smbkc_chla)
chla_reg_plot(smbkc_chla, indicator)
```

**Spring_Chlorophylla_Biomass_WCGOA_Satellite**

**Spring_Chlorophylla_Peak_EGOA_Satellite**

**Spring_Chlorophylla_Peak_SEBS_Satellite**

**Spring_Chlorophylla_Peak_WCGOA_Satellite**

**Recalculate ESP indices**
```{r}

```