---
title: "chl-indicator-comparison-calculations"
author: "Matt Callahan"
date: "6/23/2022"
output: html_document
---

The actual calculations of the ESP indicators are performed here. First we will recalculate previously submitted indicators with MODIS data to ensure that we are using the correct processes. Then we will apply the same code to the OC-CCI data. We will compare indicators visually by plotting indicator values over time and against each other, and statistically with simple linear models.

We will also explore ESR chlorophyll indicators, starting with the Southeastern Bering Sea.


## Load data

```{r, warning=FALSE, message=FALSE}
library(tidync)
library(tidyverse)
library(lubridate)
library(sf)
library(httr)
library(flextable)
library(marmap)
```

**MODIS**
MODIS data were downloaded from a google folder where Jordan stored them from previous efforts https://drive.google.com/drive/u/1/folders/1mhwQ70mjLrkiQYiQ2oNHx08Q7IlL8Q3-

```{r}
#EBS
mod_ebs<-readRDS("Data/MODIS/merged_8day_2003_2021_EBS.RDS")
#GOA
mod_goa<-readRDS("Data/MODIS/merged_8day_2003_2021_GOA.RDS")
```

**Load oc-cci**
This took a couple hundred lines of codes to make, found in chla-indicator-comparison-data.Rmd
```{r}
occ_esp<-readRDS("Data/OCCCI/occ8_esp_strata.RDS")
```


## ESP indicators
These indicators were requested by stock assessment authors. Each indicator is a single value for each year.

**Previous ESP Indicator descriptions**
```{r}
#check which indicators were used
ind <- httr::content(httr::GET("https://apex.psmfc.org/akfin/data_marts/akmp/esp_indicators?"),
                      type = "application/json"
) %>%
  dplyr::bind_rows()

ind<-ind%>%filter(grepl('Chlorophylla', INDICATOR_NAME))

#all ours?
unique(ind$CONTACT) #yes

#Descriptions
ind%>%group_by(INDICATOR_NAME)%>%
  summarise(descritption=unique(PRODUCT_DESCRIPTION),
            submission_year=unique(SUBMISSION_YEAR))%>%
   flextable()%>%
  theme_box()

```

**functions**
Create functions for 

-comparing MODIS indicators with previous indicators
-joining MODIS and OC indicators
-plotting MODIS and OC indicators over time
-plotting MODIS and OC against each other 

```{r}
#Calculation will differ for each indicator so probably not worth functionalizing that. 

#Compare MODIS with previous indicator
#indicator is the INDICATOR_NAME in the ind object
#x is the data frame with the new MODIS indicator
pull_ind<-function(indicator, x) {
  ind%>%filter(INDICATOR_NAME==indicator)%>%
  dplyr::select(YEAR, DATA_VALUE)%>%
  left_join(x, by="YEAR")%>%
  mutate(diff=round(DATA_VALUE-MODIS_VALUE,2))%>%
    print()
}
#sum of differences
sumdiff<-function(x) {
  sum(x$diff)
}

#join
chla_join<-function(oc,mod) {
  occci%>% left_join(mod, by=c("year"="YEAR"))
}

#plot over time
chla_timeplot<-function(x, indicator) {
  x%>%
  ggplot()+
  geom_line(aes(x=year,y=OCCCI_VALUE), color="red")+
  geom_line(aes(x=year,y=MODIS_VALUE), color="blue")+
  ylab("chla")+
  ggtitle(paste(indicator, " OC-CCI=red, MODIS=blue"))
}

#equation functions
lm_eqn <- function(df){
    m <- lm(OCCCI_VALUE ~ MODIS_VALUE, df);
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
         list(a = format(unname(coef(m)[1]), digits = 2),
              b = format(unname(coef(m)[2]), digits = 2),
             r2 = format(summary(m)$r.squared, digits = 3)))
    as.character(as.expression(eq));
}

chla_reg_plot<-function(df, indicator){
  ggplot(data=df, aes(x=MODIS_VALUE, y=OCCCI_VALUE, label=year))+
    geom_point()+
    geom_text()+
    geom_smooth(method="lm")+
    annotate(geom='text', label = lm_eqn(df), parse = TRUE, x=-Inf, y=Inf, hjust=0, vjust=1)+
    ggtitle(indicator)+
    geom_abline(slope=1, intercept=0, lty=2)
    
}

```

**AMJ_Chlorophylla_Biomass_SEBS_Satellite**

```{r}
#define indicator
indicator<-"AMJ_Chlorophylla_Biomass_SEBS_Satellite"
#MODIS
#recalculate indicator
mod_AMJ_SEBS <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(bsierp_name== "North middle shelf" & month%in%c(4:6)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_AMJ_SEBS)
#Values different. Follow up with Jens

```


**Spring_Chlorophylla_Biomass_EGOA_Satellite**
```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_EGOA_Satellite"
#MODIS
#recalculate indicator
mod_SPR_EGOA_B <- mod_goa %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(nmfsarea %in% c(640,650) & month==5 & depth<(-10) & depth>(-200)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_SPR_EGOA_B)
sumdiff(temp)

#Curious that this matches exactly when the indicator description says it uses oc-cci

#OCC
occci_SPR_EGOA_B<-occ_esp%>%
  filter(NMFS_REP_AREA%in% c(640, 650) & month==5 & depth<(-10) & depth>(-200))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#compare this to indicator
ind%>%filter(INDICATOR_NAME==indicator)%>%
  dplyr::select(YEAR, DATA_VALUE)%>%
  left_join(occci_SPR_EGOA_B, by=c("YEAR"="year"))%>%
  mutate(diff=round(DATA_VALUE-OCCCI_VALUE))%>%
    print()
#Nope...

#join
SPR_EGOA_B_chla<-chla_join(occci_SPR_EGOA_B, mod_SPR_EGOA_B)

#plot
#timeseries
chla_timeplot(SPR_EGOA_B_chla, indicator)

#regression
fit<-lm_eqn(SPR_EGOA_B_chla)
chla_reg_plot(SPR_EGOA_B_chla, indicator)


```

**Spring_Chlorophylla_Biomass_SEBS_Inner_Shelf_Satellite**
```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_SEBS_Inner_Shelf_Satellite"
#MODIS
#recalculate indicator
mod_BB <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(crab=="BristolBay" & month%in%c(4:6)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_BB)
sumdiff(temp)

#OCcci
occci_BB<-occ_esp%>%
  filter(BS_KING=="BBRKC" & month%in%c(4:6))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#join
BB_chla<-chla_join(occci_BB, mod_BB)

#plot
#timeseries
chla_timeplot(BB_chla, indicator)

#regression
fit<-lm_eqn(BB_chla)
chla_reg_plot(BB_chla, indicator)
```

**Spring_Chlorophylla_Biomass_SEBS_Satellite**
```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_SEBS_Satellite"
#MODIS
#recalculate indicator
mod_SEBS5 <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(Ecosystem_sub=="Southeastern Bering Sea" & month==5) %>%
  #filter(bsierp_name== "North middle shelf" & month%in%c(4:6)) %>%
  group_by(YEAR, stat_area) %>%
  summarise(MODIS_INTERMEDIATE=mean(chlorophyll,na.rm=TRUE))%>%
  group_by(YEAR)%>%
  summarise(MODIS_VALUE=mean(MODIS_INTERMEDIATE,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_SEBS5)
#Values different. Follow up with Jens


```

**Spring_Chlorophylla_Biomass_SMBKC_Satellite**
Calculations from https://github.com/jordanwatson/ESP_Indicators/blob/main/ESP_Chlorophyll_Crab.R

```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_SMBKC_Satellite"
#MODIS
#recalculate indicator
mod_smbkc <- mod_ebs %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(crab=="StMatts" & month%in%c(4:6)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_smbkc)
sumdiff(temp)

#OCcci
occci_smbkc<-occ_esp%>%
  filter(BS_KING=="StMattBKC" & month%in%c(4:6))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))

#join
smbkc_chla<-chla_join(occci_smbkc, mod_smbkc)

#plot
#timeseries
chla_timeplot(smbkc_chla, indicator)

#regression
fit<-lm_eqn(smbkc_chla)
chla_reg_plot(smbkc_chla, indicator)
```

**Spring_Chlorophylla_Biomass_WCGOA_Satellite**

```{r}
#define indicator
indicator<-"Spring_Chlorophylla_Biomass_WCGOA_Satellite"
#MODIS
#recalculate indicator
mod_SPR_WCGOA_B <- mod_goa %>%
  mutate(month=month(date),
         YEAR=year(date)) %>%
  filter(nmfsarea %in% c(610, 620, 630) & month==5 & depth<(-10) & depth>(-200)) %>%
  group_by(YEAR) %>%
  summarise(MODIS_VALUE=mean(chlorophyll,na.rm=TRUE))

#join with previous indicator and compare
temp<-pull_ind(indicator, mod_SPR_WCGOA_B)
sumdiff(temp)

#Close but not quite... Won't be a big deal if we switch out products, if we stick with MODIS it will probably be worth tracking down that difference. 

#OCC
occci_SPR_WCGOA_B<-occ_esp%>%
  filter(NMFS_REP_AREA%in% c(610, 620, 630) & month==5 & depth<(-10) & depth>(-200))%>%
   group_by(year) %>%
  summarise(OCCCI_VALUE=mean(chlorophyll,na.rm=TRUE))


#join
SPR_WCGOA_B_chla<-chla_join(occci_SPR_WCGOA_B, mod_SPR_WCGOA_B)

#plot
#timeseries
chla_timeplot(SPR_WCGOA_B_chla, indicator)

#regression
fit<-lm_eqn(SPR_WCGOA_B_chla)
chla_reg_plot(SPR_WCGOA_B_chla, indicator)


```

**Spring_Chlorophylla_Peak_EGOA_Satellite**

**Spring_Chlorophylla_Peak_SEBS_Satellite**

**Spring_Chlorophylla_Peak_WCGOA_Satellite**

**Recalculate ESR indices**
This is just a first draft. The calculation includes BSIERP South Middle shelf, Alaska Peninsula, Pribilofs, and Central Middle Shelf. 
```{r}
#Select SEBS shelf BS regions
#MODIS
mod_esr<-mod_ebs%>%
  mutate(month=month(date),
         YEAR=year(date),
         doy=yday(date)) %>%
  filter(bsierp_id %in% c(1,3,5,6) & month %in% c(4,5,6))%>%
  group_by(YEAR, doy)%>%
  summarise(MODIS_VALUE=round(mean(chlorophyll, na.rm=T),2))

#oc-cci
#MODIS
occci_esr<-occ_esp%>%
  filter(BSIERP_ID %in% c(1,3,5,6) & month %in% c(4,5,6))%>%
  mutate(doy=yday(date),
         YEAR=year) %>%
  group_by(YEAR, doy)%>%
  summarise(OCCCI_VALUE=round(mean(chlorophyll, na.rm=T),2))

#plot
ggplot()+
  geom_line(data=occci_esr, aes(x=doy, y=OCCCI_VALUE), color="red")+
  geom_line(data=mod_esr, aes(x=doy, y=MODIS_VALUE), color="blue")+
  facet_wrap(~YEAR, ncol=4)

#save files for Jens
#saveRDS(mod_esr, "Data/MODIS/modis_south_middle_shelf.RDS")
#saveRDS(mod_esr, "Data/OCCCI/occci_south_middle_shelf.RDS") 
#and grouped by stat areas
#MODIS
#mod_ebs%>%
#  mutate(month=month(date),
#         YEAR=year(date)) %>%
#  filter(bsierp_id %in% c(1,3,5,6) & month %in% c(4,5,6))%>%
#  group_by(YEAR, date, stat_area)%>%
#  summarise(MODIS_VALUE=round(mean(chlorophyll, na.rm=T),2))%>%
#  saveRDS("Data/MODIS/MODIS_SEBS_shelf_stat_esr.RDS")
#OC-CCI
#MODIS
#occ_esp%>%
#  filter(BSIERP_ID %in% c(1,3,5,6) & month %in% c(4,5,6))%>%
#  group_by(year, date, STAT_AREA)%>%
#  summarise(OCCCI_VALUE=round(mean(chlorophyll, na.rm=T),2))%>%
#  saveRDS("Data/OCCCI/OCCI_SEBS_shelf_stat_esr.RDS")
```