---
title: "OC-CCI QA"
author: "Matt Callahan"
date: "7/12/2022"
output: html_document
---

## Overview
Here I do a few QA tests on the OC-CCI data to ensure that our data pull process has correctly extracted data. 

## Test point in polygon
I will pick a region (we'll do NMFS 516) and redo the point in polygon operation for two years (2020 and 2010) and compare record counts and results to those from our lookup table. 

**point in polygon**
We will use the same process in sf that was used to create the lookup table.
```{r, warning=FALSE, message=FALSE}
#install packages
library(tidyverse)
library(lubridate)
library(sf)
library(AKmarineareas)
library(tidync)
```

```{r}
#import 2020 and 2010 data from oc-cci processed file 
occci_lkp<-readRDS("Data/OCCCI/occ8_esp_strata.RDS")%>%filter(year %in% c(2010, 2020) & NMFS_REP_AREA == 516)

#bring in NMFS area
nmfs<-AK_marine_area()%>%filter(NMFS_REP_AREA == "516")%>%
  dplyr::select(NMFS_REP_AREA)

#bring in unprocessed data from netcdfs
#tidync function
tidy_chl<-function(file) {
  tidync(file) %>% 
  hyper_tibble()%>% 
  mutate(date=as_datetime(time),
         chlorophyll=round(chlor_a,3),
         year=year(date),
         month=month(date))%>%
  dplyr::select(!c(time, chlor_a))
}

occci_2010<-tidy_chl("Data/OCCCI/occ8_2010.nc")
occci_2020<-tidy_chl("Data/OCCCI/occ8_2020.nc")



#convert occci to spatial object
occci_2010<-occci_2010%>%
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326, agr = 'constant')
occci_2020<-occci_2020%>%
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326, agr = 'constant')

#join
occci_2010<-occci_2010%>%
  st_join(nmfs, join = st_within)%>%
  filter(NMFS_REP_AREA == "516")

occci_2020<-occci_2020%>%
  st_join(nmfs, join = st_within)%>%
  filter(NMFS_REP_AREA == "516")

#compare record counts
nrow(occci_2010)-nrow(occci_lkp%>%filter(year==2010))
nrow(occci_2020)-nrow(occci_lkp%>%filter(year==2020))
#close... why not exact?

#plot
ggplot()+
  geom_sf(data=nmfs, fill=NA)+
  geom_sf(data=occci_2010, color="red")+
  geom_point(data=occci_lkp%>%filter(year==2010), aes(x=longc, y=latc), color="black")
#why are those points there in 2010 but not 2020???
ggplot()+
  geom_sf(data=nmfs, fill=NA)+
  geom_sf(data=occci_2010, color="red")+
  geom_point(data=occci_lkp%>%filter(year==2010), aes(x=longc, y=latc), color="black")+
  ylim(c(55,56))
#plot for 2020
ggplot()+
  geom_sf(data=nmfs, fill=NA)+
  geom_sf(data=occci_2020, color="red")+
  geom_point(data=occci_lkp%>%filter(year==2020), aes(x=longc, y=latc), color="black")+
  ylim(c(55,56))
```

Bring in depth da
```{r}

#maybe they're really close to land and we cut them out...?
ggplot()+
  geom_sf(data=nmfs, fill=NA)+
  geom_sf(data=occci_2010, aes(color=ifelse(depth>0, "red", "green")))+
  #geom_point(data=occci_lkp%>%filter(year==2010), aes(x=longc, y=latc), color="black")+
  ylim(c(55,56))

```

## Spherical geometry
I've had to turn off spherical geometry (for some reason) to do point in polygon operations in the past. I will rerun the point in polygon to make sure that it doesn't alter the results.

```{r}
#if it an issue with spherical geometry?
#unneccessary but comforting
#Turn off spherical geometry

sf::sf_use_s2(FALSE)

#reload
occci_2010_nsg<-tidy_chl("Data/OCCCI/occ8_2010.nc")
occci_2020_nsg<-tidy_chl("Data/OCCCI/occ8_2020.nc")

#convert occci to spatial object
occci_2010_nsg<-occci_2010_nsg%>%
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326, agr = 'constant')
occci_2020_nsg<-occci_2020_nsg%>%
  st_as_sf(coords = c('longitude', 'latitude'), crs = 4326, agr = 'constant')

occci_2010_nsg<-occci_2010_nsg%>%
  st_join(nmfs, join = st_within)%>%
  filter(NMFS_REP_AREA == "516")

occci_2020_nsg<-occci_2020_nsg%>%
  st_join(nmfs, join = st_within)%>%
  filter(NMFS_REP_AREA == "516")

#compare record counts
sum(nrow(occci_2010_nsg), nrow(occci_2020_nsg))-nrow(occci_lkp)
nrow(occci_2010)-nrow(occci_2010)
nrow(occci_2020)-nrow(occci_2020)
#That wasn't the issue (phew!!!)

```

